Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-17 thesis/acknowledgments.tex
remvoing space

To my wife Ellen, who moved across the country for me to NYC
(and across the country again in the next few months), who has patiently put up with
all of my travel and time away at conferences in the past few years,
who has worked longer hours at much more demanding jobs than the work I have put
into this \dissertation, and who has continued to support me through this
entire journey, all just so that I could pursue my dream. A simple ``thank you" is
entirely insufficient to repay her for these sacrifices, but its a good thing
I have the rest of my life to show how grateful I am.

>>>>

To my wife Ellen, who moved across the country for me to NYC
(and across the country again in the next few months), who has patiently put up with
all of my travel and time away at conferences in the past few years,
who has worked longer hours at much more demanding jobs than the work I have put
into this \Dissertation, and who has continued to support me through this
entire journey, all just so that I could pursue my dream. A simple ``thank you" is
entirely insufficient to repay her for these sacrifices, but its a good thing
I have the rest of my life to show how grateful I am.
